Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-04-30 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Final version with corrections made

funding: |
  Please add: "This research received no external funding" or "This research 
  was funded by NAME OF FUNDER grant number XXX."  and ``The APC was funded 
  by XXX''. Check carefully that the details given are accurate and use the 
  standard spelling of funding agency names at 
  \url{https://search.crossref.org/funding}, any errors may affect your future 
  funding.
institutionalreview: |
 Not applicable.
#informedconsent: |
  # Any research article describing a study involving humans should contain this 
  # statement. Please add ``Informed consent was obtained from all subjects 
  # involved in the study.'' OR ``Patient consent was waived due to REASON 
  # (please provide a detailed justification).'' OR ``Not applicable'' for 
  # studies not involving humans. You might also choose to exclude this statement 
  # if the study did not involve humans.

  # Written informed consent for publication must be obtained from participating 
  # patients who can be identified (including by the patients themselves). Please 
  # state ``Written informed consent has been obtained from the patient(s) to 
  # publish this paper'' if applicable.
dataavailability: |
  The Sentinel-1  images are made publicly available by European Space Agency via Copernicus Data Space Ecosystem at \url{https://dataspace.copernicus.eu/} (accessed on 24 April 2024).
conflictsofinterest: |
  The authors declare no conflict of interest.
supplementary: |
 This article was written in Rmarkdown and is fully reproducible. The code and data are accessible at
 \url{https://github.com/rjaneth/identifying-heterogeneity-in-sar-data-with-new-test-statistics} (accessed on 24 April 2024).
# abbreviations:
#   - short: MDPI
#     long: Multidisciplinary Digital Publishing Institute
#   - short: DOAJ
#     long: Directory of open access journals
#   - short: TLA
#     long: Three letter acronym
#   - short: LD 
#     long: linear dichroism

header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{xcolor}
   - \usepackage{amsmath}
   - \usepackage{multirow}
   - \usepackage{subcaption}
   - \captionsetup[sub]{labelfont=bf,textfont=bf}

@@

The coefficient of variation (CV), introduced in 1896 by Pearson&nbsp;\cite{Pearson1896}, is a relative dispersion measure widely used in various fields of applied statistics, including sampling, biostatistics, medical and biological research, climatology and other fields&nbsp;\cite{hendricks1936sampling,Tian2005,SubrahmanyaNairy2003,Chankham2024}.
It facilitates the comparison of variability between different populations and is particularly valuable for relating variables with different units. 
This is because when the main purpose is to compare the variations of several variables, the standard deviation can only serve as an adequate measure of variation if all variables are expressed in the same unit of measurement and have identical means. 
If these conditions are not met, then the CV is the relative measure that is usually used in real applications. 
The variable with the highest CV value is the one with the largest relative dispersion around the mean value&nbsp;\cite{Banik2011}.
The coefficient of variation is the basic measure of heterogeneity in SAR data&nbsp;\cite{oliverquegan98}.
We study two ways of estimating the coefficient of variation.

@@

```{r Plot_GI0_to_gamma1, echo=FALSE, message=FALSE, warning=FALSE, out.width="70%", fig.show="hold", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ with $L=8$."}

@@

Several authors&nbsp;\cite{vasicek1976test, Wieczorkowski1999,correa1995new,AlOmari2019} have studied the problem of the non-parametric estimation of $H(Z)$.
Their proposals use estimators based on differences between order statistics: spacings.

@@

* Al-Omari&nbsp;\cite{IbrahimAlOmari2014}:
$$
\widehat{H}_{\text{AO}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{\omega_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right]
$$
where
$$
\omega_i= \begin{cases}3/2 & \text { if }\quad 1 \leq i \leq m, \\ 2 & \text { if }\quad m+1 \leq i \leq n-m, \\ 3/2 & \text { if } \quad n-m+1 \leq i \leq n,\end{cases}
$$
in which $Z_{(i-m)}=Z_{(1)}$ for $i \leq m$, and $Z_{(i+m)}=Z_{(n)}$ for $i \geq n-m$.

@@

Let us assume that the non-parametric entropy estimator
\(\widehat{H}=\widehat{\theta}(\bm{Z})\) is inherently biased, i.e,:
\begin{equation}
\label{Eq:bias1}
\operatorname{Bias}\big(\widehat{\theta}(\bm{Z})\big) = E\big[\widehat{\theta}(\bm{Z})\big] - \theta \neq 0.
\end{equation} 
Our bootstrap-improved estimator is of the form:
\begin{align*}
\widetilde{H} &= 2\widehat{\theta}(\bm{Z}) - \frac{1}{B}\sum_{b=1}^B \widehat{\theta}_b(\bm{Z}^{(b)}),
\end{align*} 
where \(B\) is the number of observations obtained by resampling from $\bm Z$ with replacement. 
Applying this methodology, the original estimators of Correa,
Ebrahimi and Al-Omari are now referred to as the proposed bootstrap-enhanced versions:
\(\widetilde{H}_{\text{C}}\),
\(\widetilde{H}_{\text{E}}\), and \(\widetilde{H}_{\text{AO}}\),
respectively.

@@

```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.pos="hbt",  fig.cap="Bias and MSE, $L=5$ and  $\\alpha=-10$.", fig.width=8, fig.height=5.5}

@@

```{r Table_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#cat("\\setlength{\\tabcolsep}{0.5pt}\n")
load("./Data/resultsgi0_1.Rdata")

@@

colnames(reshaped_results) <- c("$\\mu$", "$n$",  "$\\widehat{H}_{\\text{C}}$", "$\\widehat{H}_{\\text{E}}$","$\\widehat{H}_{\\text{AO}}$",  "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$","$\\widetilde{H}_{\\text{AO}}$",   "$\\widehat{H}_{\\text{C}}$", "$\\widehat{H}_{\\text{E}}$","$\\widehat{H}_{\\text{AO}}$", "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$","$\\widetilde{H}_{\\text{AO}}$")

@@

#print(
 # kbl(
knitr::kable(
    reshaped_results,
    caption = "Bias and MSE of non-parametric entropy estimators and bootstrap versions.",
    format = "latex",
    booktabs = TRUE,
    align = "lrrrrrrrrrrrrrrr",
    escape = FALSE, 
    digits = 2,  
    label = "table2",
    centering = FALSE,
    table.envir = "table", position = "H") %>%
    add_header_above(c(" ", " ", "Bias" = 6,  "MSE" = 6)) %>%
    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
    row_spec(0,  align = "c")%>%
    kable_styling(latex_options = "scale_down")
  #)
  #kable_styling(latex_options = c("scale_down"))

@@

For a random sample \(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) from a distribution $\mathcal{D}$, a test statistic is proposed. It is based on an  empirical distribution that arises  from the difference between non-parametrically estimated entropies $\widetilde{H}(\bm{Z})$ and the analytical entropy of Gamma SAR&nbsp;\eqref{E:E-gamma} evaluated at the logarithm of the sample mean, where $L_0\geq 1$ is known.

Hence, the entropy-based test statistic is defined as:
\begin{equation}
\label{Eq:test_e}
S(\bm{Z};L_0)= \widetilde{H}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L_0)+\ln \widebar{\bm{Z}}\right].
\end{equation}

This test statistic  aims to assess the behavior of the data under the null hypothesis using the empirical distribution.
If the data represent fully-developed speckle, the density should center around zero, i.e., $S(\bm{Z};L_0)\approx 0$. Otherwise, under the alternative hypothesis, the empirical distribution would shift from zero, suggesting significant differences and implying the presence of heterogeneous clutter.

@@

Figure&nbsp;\ref{fig:Plot_density} shows the empirical test statistic densities for different sample sizes using \(\widetilde{H}_{\text{AO}}\) estimator, and Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean, 
standard deviation&nbsp;(SD), 
variance&nbsp;(Var), 
skewness&nbsp;(SK), 
excessive kurtosis&nbsp;(EK) and 
Anderson--Darling \(p\) values for normality. 
Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption.
A low variance as well as a skewness and an excessive kurtosis of almost zero indicate limited dispersion, asymmetry and a light tail.
Normal QQ plots confirm that there is no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.

@@

R <- 2000
mu <- 1
B <- 50

sample.size <- c(25,49, 81, 121)
L_values <- c(3,  5, 8, 11)

@@

```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.pos="hbt",  fig.cap="Empirical density  under the null hypothesis.", fig.width=6, fig.height=5.0}

@@

  p <- ggplot(combined_data, aes(x = Test_Statistics, col = factor(SampleSize), linetype = factor(SampleSize))) +
    geom_line(stat = "density", linewidth = 1.0) +
    scale_color_viridis(discrete = TRUE, option = "C", direction = -1, begin = 0.1, end = 0.8, name = "Sample Size") +
    scale_linetype_manual(values = rep("solid", length(sample.size)), name = "Sample Size") +
    labs(x = "Test Statistics", y = "Density") +
    ggtitle(bquote(italic(L) == .(L))) +
    theme(plot.title = element_text(hjust = 0.5))#titulo centrado

@@

table_result_combined <- knitr::kable(
  combined_summary_stats,
  caption = "Descriptive analysis of $S(\\bm Z; L)$ with $L\\in\\left\\{3,5, 8,11\\right\\}$ and $\\mu=1$.",
  format = "latex",
  booktabs = TRUE,
  align = "lrrrrrrr",
  escape = FALSE,
  digits = 4,
  label = "table_stat_combined",
  centering = FALSE,
  table.envir = "table", position = "H") %>%
  #table.env = 'table*' # to span multiple columns
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")

@@

```{r Plot_normality_qq, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.pos="hbt",  fig.cap="Normal QQ-plots for  $n=121$.", fig.width=6, fig.height=5}

@@

After checking the normality of the test statistics, we examined the possibilities of the proposed test in terms of size and power.
Under \(\mathcal{H}_0\), the distribution of the test statistic is asymptotically normal.
Therefore, the \(p\) value is calculated as
\(2\Phi(-|\varepsilon|)\), where \(\Phi\) is the standard
Gaussian cumulative distribution function, and \(\varepsilon\) is the standardized test statistic given by :
\[
\varepsilon=\frac{\widetilde{H}-H_{\Gamma_{\text{SAR}}}}{\widehat\sigma}.
\]

We have nominal levels of \SI{1}{\percent}, \SI{5}{\percent}, and
\SI{10}{\percent}. 
In terms of size, \(1000\) simulations were used for different sample sizes from the $\Gamma_{\text{SAR}}$ distribution, with different values of $L$,  $\mu=1$ and \(\widetilde{H}_{\text{AO}}\) estimator. 
In all cases, the nominal level was achieved. 
We assessed the test power using \(1000\) simulations for different sample sizes from the $G_I^0$ distribution, with  $\mu=1$, $\alpha=-2$, and \(\widetilde{H}_{\text{AO}}\) estimator.
The power generally improves with increasing sample size and number of looks.
The results are shown in Table&nbsp;\ref{tab:table_size_power}.
<!-- ACF Please clarify which alternatives you used for the power -->
<!-- JA Corrected -->

@@

In addition to the entropy-based test, we also propose a test statistic based on the classical CV. This test statistic is defined as follows:
\begin{align}
	T_{\text{CV}}=\frac{S}{\widebar{Z}},
\end{align}
where $S$ and $\widebar{Z}$ are the sample standard deviation and the sample mean, respectively.

@@

The AIC and BIC results in Tables&nbsp;\ref{tab:table_aic_gamma}--\ref{tab:table_aic_gio_MnADmedian} indicate that the CV and \(\text{CV}_{\text{MnAD}}\) data from different distributed Gamma and \(G_I^0\) synthetic sample sizes match the properties of an LN distribution.
It is important to note that this conclusion was drawn empirically based on a dictionary of distributions that are analytically tractable and well-defined under biparametric, unimodal, asymmetric, and positive distributions.

@@

table_result_combined <- knitr::kable(
  combined,
  caption = "AIC and BIC values for evaluating the best distribution with CV data from Gamma SAR.",
  format = "latex",
  booktabs = TRUE,
  align = "lccccccc",
  escape = FALSE,
  digits = 2,
  label = "table_aic_gamma",
  centering = FALSE,
  table.envir = "table", position = "H") %>%
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")

@@

table_result_combined <- knitr::kable(
  combined,
  caption = "AIC and BIC values for evaluating the best distribution with CV data from $G_I^0$.",
  format = "latex",
  booktabs = TRUE,
  align = "lccccccc",
  escape = FALSE,
  digits = 2,
  label = "table_aic",
  centering = FALSE,
  table.envir = "table", position = "H") %>%
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")

@@

sample.size <- c(49)
R <- 15000
mu <- 1
L <- 5
B <- 5
alpha1 <- -2

@@

```{r Plot_cv_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with CV data from Gamma SAR, with  $n=49$, $L=5$ and $\\mu=1$.", fig.width=8, fig.height=6}

>>>>

funding: |
  This research received no external funding.
institutionalreview: |
 Not applicable.
#informedconsent: |
  # Any research article describing a study involving humans should contain this 
  # statement. Please add ``Informed consent was obtained from all subjects 
  # involved in the study.'' OR ``Patient consent was waived due to REASON 
  # (please provide a detailed justification).'' OR ``Not applicable'' for 
  # studies not involving humans. You might also choose to exclude this statement 
  # if the study did not involve humans.

  # Written informed consent for publication must be obtained from participating 
  # patients who can be identified (including by the patients themselves). Please 
  # state ``Written informed consent has been obtained from the patient(s) to 
  # publish this paper'' if applicable.
dataavailability: |
  The Sentinel-1  images are made publicly available by European Space Agency via Copernicus Data Space Ecosystem at \url{https://dataspace.copernicus.eu/} (accessed on 24 April 2024).
conflictsofinterest: |
  The authors declare no conflict of interest.
supplementary: |
 This article was written in Rmarkdown and is fully reproducible. The code and data are accessible at
 \url{https://github.com/rjaneth/identifying-heterogeneity-in-sar-data-with-new-test-statistics} (accessed on 30 April 2024).
# abbreviations:
#   - short: MDPI
#     long: Multidisciplinary Digital Publishing Institute
#   - short: DOAJ
#     long: Directory of open access journals
#   - short: TLA
#     long: Three letter acronym
#   - short: LD 
#     long: linear dichroism

header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{xcolor}
   - \usepackage{amsmath}
   - \usepackage{multirow}
   - \usepackage{subcaption}
   - \captionsetup[subfigure]{labelformat=parens, justification=centering}
   - \usepackage{placeins}

@@

The coefficient of variation (CV), introduced in 1896 by Pearson&nbsp;\cite{Pearson1896}, is a relative dispersion measure widely used in various fields of applied statistics, including sampling, biostatistics, medical and biological research, climatology and other fields&nbsp;\cite{hendricks1936sampling,Tian2005,SubrahmanyaNairy2003,Chankham2024}.
It facilitates the comparison of variability between different populations and is particularly valuable for relating variables with different units. 
This is because when the main purpose is to compare the variations of several variables, the standard deviation can only serve as an adequate measure of variation if all variables are expressed in the same unit of measurement and have identical means. 
If these conditions are not met, then the CV is the relative measure that is usually used in real applications. 
The variable with the highest CV value is the one with the largest relative dispersion around the mean value&nbsp;\cite{Banik2011}.
The coefficient of variation is the basic measure of heterogeneity in SAR data&nbsp;\cite{Touzi1988,oliverquegan98}.
We study two ways of estimating the coefficient of variation.

@@

```{r Plot_GI0_to_gamma1, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="80%",  fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$, with $L=8$."}

@@

The problem of the non-parametric estimation of $H(Z)$ has been studied by many authors, including&nbsp;\cite{vasicek1976test,Wieczorkowski1999,correa1995new,AlOmari2019}.
Their proposals use estimators based on differences between order statistics: spacings.

@@

* Al-Omari&nbsp;\cite{IbrahimAlOmari2014}:
$$
\widehat{H}_{\text{AO}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{\omega_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
$$
where
$$
\omega_i= \begin{cases}3/2 & \text { if }\quad 1 \leq i \leq m, \\ 2 & \text { if }\quad m+1 \leq i \leq n-m, \\ 3/2 & \text { if } \quad n-m+1 \leq i \leq n,\end{cases}
$$
in which $Z_{(i-m)}=Z_{(1)}$ for $i \leq m$, and $Z_{(i+m)}=Z_{(n)}$ for $i \geq n-m$.

@@

Let us assume that the non-parametric entropy estimator
\(\widehat{H}=\widehat{\theta}(\bm{Z})\) is inherently biased, i.e,:
\begin{equation}
\label{Eq:bias1}
\operatorname{Bias}\big(\widehat{\theta}(\bm{Z})\big) = E\big[\widehat{\theta}(\bm{Z})\big] - \theta \neq 0.
\end{equation} 
Our bootstrap-improved estimator is of the form:
\begin{align*}
\widetilde{H} &= 2\widehat{\theta}(\bm{Z}) - \frac{1}{B}\sum_{b=1}^B \widehat{\theta}_b(\bm{Z}^{(b)}),
\end{align*} 
where \(B\) is the number of observations obtained by resampling from $\bm Z$ with replacement. 
Applying this methodology, the original estimators of Correa,
Ebrahimi and Al-Omari are now referred to as the proposed bootstrap-improved versions:
\(\widetilde{H}_{\text{C}}\),
\(\widetilde{H}_{\text{E}}\), and \(\widetilde{H}_{\text{AO}}\),
respectively.

@@

```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="95%", fig.pos="hbt",  fig.cap="Bias and MSE, $L=5$ and  $\\alpha=-10$."}

@@

```{r Table_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
cat("\\setlength{\\tabcolsep}{6pt}\n")
load("./Data/resultsgi0_1.Rdata")

@@

colnames(reshaped_results) <- c("$\\bm{\\mu}$", "$\\bm{n}$",  "$\\bm{\\widehat{H}_{\\text{C}}}$", "$\\bm{\\widehat{H}_{\\text{E}}}$","$\\bm{\\widehat{H}_{\\text{AO}}}$",  "$\\bm{\\widetilde{H}_{\\text{C}}}$", "$\\bm{\\widetilde{H}_{\\text{E}}}$","$\\bm{\\widetilde{H}_{\\text{AO}}}$",   "$\\bm{\\widehat{H}_{\\text{C}}}$", "$\\bm{\\widehat{H}_{\\text{E}}}$","$\\bm{\\widehat{H}_{\\text{AO}}}$", "$\\bm{\\widetilde{H}_{\\text{C}}}$", "$\\bm{\\widetilde{H}_{\\text{E}}}$","$\\bm{\\widetilde{H}_{\\text{AO}}}$")

@@

#print(
 # kbl(
knitr::kable(
    reshaped_results,
    caption = "Bias and MSE of non-parametric entropy estimators and bootstrap versions.",
    format = "latex",
    booktabs = TRUE,
    align = "crllllllllllll",
    escape = FALSE, 
    digits = 2,  
    label = "table2",
    centering = FALSE,
    table.envir = "table",  position="hbt", linesep = "") %>%
    add_header_above(c(" ", " ", "Bias" = 6,  "MSE" = 6)) %>%
    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
    row_spec(0,  align = "r")%>%
    kable_styling(latex_options = "scale_down")#%>%
   # kable_styling( full_width = T)
  #)
  #kable_styling(latex_options = c("scale_down"))

@@

For a random sample \(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) from a distribution $\mathcal{D}$, a test statistic is proposed. It is based on an  empirical distribution that arises  from the difference between non-parametrically estimated entropies $\widetilde{H}(\bm{Z})$ and the analytical entropy of $\Gamma_{\text{SAR}}$&nbsp;\eqref{E:E-gamma} evaluated at the logarithm of the sample mean, where $L\geq 1$ is known.

Hence, the entropy-based test statistic is defined as:
\begin{equation}
\label{Eq:test_e}
S(\bm{Z};L)= \widetilde{H}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{\bm{Z}}\right].
\end{equation}

This test statistic  aims to assess the behavior of the data under the null hypothesis using the empirical distribution.
If the data represent fully-developed speckle, the density should center around zero, i.e., $S(\bm{Z};L)\approx 0$. Otherwise, under the alternative hypothesis, the empirical distribution would shift from zero, suggesting significant differences and implying the presence of heterogeneous clutter.

@@

The comparison between the bootstrap-improved estimators is shown in Table&nbsp;\ref{tab:table_time}, where the test accuracy under null hypothesis is presented alongside running times. 
The test accuracy is evaluated through 1000 simulated samples of different sizes, with each size replicated 100 times using bootstrap resampling.

The processing time is an important feature, especially considering the application of these estimators to large datasets of SAR images, as can be seen in Section&nbsp;\ref{sec:Results}.

```{r Simulated_comparative_time2, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")

R <- 1000
mu <- 1
B <- 40#100

sample.size <- c(25,49, 81, 121)
L_values <- c( 2, 8)

bootstrap_estimators <- list(
  "$\\widetilde{H}_{\\text{C}}$" = bootstrap_correa_estimator,
  "$\\widetilde{H}_{\\text{E}}$" = bootstrap_ebrahimi_estimator,
  "$\\widetilde{H}_{\\text{AO}}$" = bootstrap_al_omari_1_estimator

)

all_TestStatistics <- list()

execution_times <- list()

for (estimator_name in names(bootstrap_estimators)) {

  TestStatistics <- list()

  for (L in L_values) {
    TestStat <- list()

    for (s in sample.size) {
      TestStat1 <- numeric(R)
      start_time <- Sys.time() # start time

      for (r in 1:R) {
        z <- gamma_sar_sample(L, mu, s)
        TestStat1[r] <- bootstrap_estimators[[estimator_name]](z, B) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
      }

      TestStatistics[[as.character(s)]] <- data.frame("SampleSize" = rep(s, R), "Test_Statistics" = TestStat1)

      end_time <- Sys.time() # end time
      execution_time <- end_time - start_time # total time
      execution_times[[paste(estimator_name, L, s)]] <- execution_time # save time
    }

    all_TestStatistics[[paste(estimator_name, L)]] <- TestStatistics
  }
}

save(all_TestStatistics, execution_times, file = "./Data/results_data_time2.Rdata")

```{r Table_statistic_time2, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

load("./Data/results_data_time2.Rdata")

combined_results <- data.frame(Estimator = character(),
                               L = numeric(),
                               SampleSize = numeric(),
                               Mean = numeric(),
                               Time = numeric())

if (length(all_TestStatistics) > 0 & length(execution_times) > 0) {
  for (estimator_name in names(bootstrap_estimators)) {
    for (L in L_values) {
      for (sample_size in sample.size) {

        if (!is.null(all_TestStatistics[[paste(estimator_name, L)]][[as.character(sample_size)]]) &
            !is.null(execution_times[[paste(estimator_name, L, sample_size)]])) {
          mean_value <- mean(all_TestStatistics[[paste(estimator_name, L)]][[as.character(sample_size)]][["Test_Statistics"]])
          time_value <- execution_times[[paste(estimator_name, L, sample_size)]]
          combined_results <- rbind(combined_results, data.frame(Estimator = estimator_name,
                                                                 L = L,
                                                                 SampleSize = sample_size,
                                                                 Mean = mean_value,
                                                                 Time = time_value))
        }
      }
    }
  }
} else {
  # 
  print("No data.")
}

# time
combined_results$Time <- gsub(" secs", "", combined_results$Time)

# 
combined_results$Time <- sprintf("%.2f", as.numeric(combined_results$Time))

#  LaTeX notation
colnames(combined_results) <- c("\\textbf{Estimator}", "$\\bm{L}$", "$\\bm{n}$", "$S(\\bm{Z}; L)$", "\\textbf{ Time} (s)")
combined_results[] <- lapply(combined_results, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.5f$", x), sprintf("$\\phantom{-}%.5f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})

#
table_result_combined <- knitr::kable(
  combined_results,
  caption = "Test accuracy and processing time for each bootstrap-improved estimator. ",
  format = "latex",
  booktabs = TRUE,
  align = "ccccccc",
  escape = FALSE,
  digits = 5,
  label = "table_time",
  centering = FALSE,
  table.envir = "table", position="H", linesep = "") %>%
  row_spec(4,  extra_latex_after = "\\cline{3-5}")%>%
  row_spec(12,  extra_latex_after = "\\cline{3-5}")%>%
  row_spec(20,  extra_latex_after = "\\cline{3-5}")%>%
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")%>%
  kable_styling(latex_options = "scale_down")%>%
  kable_styling( full_width = T)#%>%
  #kable_styling(latex_options = c("repeat_header"))

As visible from Table&nbsp;\ref{tab:table_time}, the accuracy of the test results across the three estimators shows similarities in certain sample sizes. 
However, practical scenarios in SAR image processing often involve small sample sizes, typically obtained over windows of size $7\times7$.  
It is also noteworthy that the \(\widetilde{H}_{\text{AO}}\) estimator exhibited the shortest processing time, followed by \(\widetilde{H}_{\text{E}}\) and \(\widetilde{H}_{\text{C}}\). Considering this aspect, we select the \(\widetilde{H}_{\text{AO}}\) estimator for subsequent simulations. Henceforth,  the test statistical &nbsp;\eqref{Eq:test_e} will be denoted as: \(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\).

We now verify the normality of the data generated by the \(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\) test.
Figure&nbsp;\ref{fig:Plot_density} shows the empirical  densities for different sample sizes  and Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean, 
standard deviation&nbsp;(SD), 
variance&nbsp;(Var), 
skewness&nbsp;(SK), 
excessive kurtosis&nbsp;(EK) and 
Anderson--Darling \(p\) values for normality. 
Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption.
A low variance as well as a skewness and an excessive kurtosis of almost zero indicate limited dispersion, asymmetry and a light tail.
Normal QQ plots confirm that there is no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.

@@

R <- 2000
mu <- 1
B <- 5

sample.size <- c(25,49, 81, 121, 200)
L_values <- c(3,  5, 8, 11)

@@

```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="95%", fig.pos="hbt",  fig.cap="Empirical density  under the null hypothesis.", fig.width=6, fig.height=5.0}

@@

  p <- ggplot(combined_data, aes(x = Test_Statistics, col = factor(SampleSize), linetype = factor(SampleSize))) +
    geom_line(stat = "density", linewidth = 1.3) +
    scale_color_viridis(discrete = TRUE, option = "C", direction = -1, begin = 0.1, end = 0.8, name = "Sample Size") +
    scale_linetype_manual(values = rep("solid", length(sample.size)), name = "Sample Size") +
    labs(x = "Test Statistics", y = "Density") +
    ggtitle(bquote(italic(L) == .(L))) +
    theme(plot.title = element_text(hjust = 0.5))#titulo centrado

@@

table_result_combined <- knitr::kable(
  combined_summary_stats,
  caption = "Descriptive analysis of $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$ with $L\\in\\left\\{3,5, 8,11\\right\\}$ and $\\mu=1$.",
  format = "latex",
  #longtable = T,
  booktabs = TRUE,
  align = "ccrrrrrr",
  escape = FALSE,
  digits = 4,
  label = "table_stat_combined",
  centering = FALSE,
  table.envir = "table", position="H", linesep = "") %>%
  #table.env = 'table*' # to span multiple columns
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")%>%
  kable_styling(latex_options = "scale_down")%>%
  kable_styling( full_width = T)%>%
  kable_styling(latex_options = c("repeat_header"))

@@

```{r Plot_normality_qq, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="90%", fig.pos="H",  fig.cap="Normal QQ-plots for  $n=121$.", fig.width=6, fig.height=5}

@@

After checking the normality of the data, we examined the possibilities of the proposed test in terms of size and power.
Under \(\mathcal{H}_0\), the distribution of the test statistic is asymptotically normal.
Therefore, the \(p\) values are calculated as
\(2\Phi(-|\varepsilon|)\), where \(\Phi\) is the standard
Gaussian cumulative distribution function, and \(\varepsilon\) is the standardized test statistic given by:
\[
\varepsilon=\frac{\widetilde{H}_{\text{AO}}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{\bm{Z}}\right]}{\widehat\sigma}.
\]

We have nominal levels of \SI{1}{\percent}, \SI{5}{\percent}, and
\SI{10}{\percent}. 
In terms of size, \(1000\) simulations were used for different sample sizes from the $\Gamma_{\text{SAR}}$ distribution, with varying values of $L$, and  $\mu=1$. 
In all cases, the nominal level was achieved. 
We assessed the test power using \(1000\) simulations for different sample sizes from the $G_I^0$ distribution, with  $\mu=1$, and $\alpha=-2$.
The power generally improves with increasing sample size and number of looks.
The results are shown in Table&nbsp;\ref{tab:table_size_power}.
<!-- ACF Please clarify which alternatives you used for the power -->
<!-- JA Corrected -->

@@

In addition to the \(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\) test, we also propose a test statistic based on the classical CV. This test statistic is defined as follows:
\begin{align}
	T_{\text{CV}}=\frac{S}{\widebar{Z}},
\end{align}
where $S$ and $\widebar{Z}$ are the sample standard deviation and the sample mean, respectively.

@@

The AIC and BIC results in Tables&nbsp;\ref{tab:table_aic_gamma}--\ref{tab:table_aic_gio_MnADmedian} indicate that the CV and \(\text{CV}_{\text{MnAD}}\) data from different distributed $\Gamma_{\text{SAR}}$ and \(G_I^0\) synthetic sample sizes match the properties of an LN distribution.
It is important to note that this conclusion was drawn empirically based on a dictionary of distributions that are analytically tractable and well-defined under biparametric, unimodal, asymmetric, and positive distributions.

@@

# LaTeX notation 
combined[] <- lapply(combined, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.1f$", x), sprintf("$\\phantom{-}%.1f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})

table_result_combined <- knitr::kable(
  combined,
  caption = "AIC and BIC values for evaluating the best distribution with CV data from $\\Gamma_{\\text{SAR}}$.",
  format = "latex",
  booktabs = TRUE,
  align = "ccccrrrrr",
  escape = FALSE,
  digits = 2,
  label = "table_aic_gamma",
  centering = FALSE,
  table.envir = "table", position = "H") %>%
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")%>%
  kable_styling(latex_options = "scale_down")%>%
  kable_styling( full_width = T)

@@

table_result_combined <- knitr::kable(
  combined,
  caption = "AIC and BIC values for evaluating the best distribution with CV data from $G_I^0$.",
  format = "latex",
  booktabs = TRUE,
  align = "cccccccc",
  escape = FALSE,
  digits = 2,
  label = "table_aic",
  centering = FALSE,
  table.envir = "table", position = "H") %>%
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")%>%
  kable_styling(latex_options = "scale_down")%>%
  kable_styling( full_width = T)

@@

sample.size <- c(49)
R <- 15000
mu <- 1
L <- 5
B <- 5
#alpha1 <- -2

@@

```{r Plot_cv_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with CV data from $\\Gamma_{\\text{SAR}}$, with  $n=49$, $L=5$ and $\\mu=1$.", fig.width=8, fig.height=6}
